Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-05 manuscript.Rmd

```{r join_sf}
travel_time_sf <- left_join(x = travel_times_census_join, y = dc_acs_tracts, by = "GEOID") %>%
	st_as_sf() %>%
	st_transform(crs = 102285)
```

@@

travel_time_sf <- travel_time_sf %>%
  mutate(distance = as.numeric(st_distance(centroids, mnm_sf$geometry, by_element = TRUE)))
```

>>>>

```{r join_sf}
centroids <- data.frame(cbind(st_coordinates(st_centroid(dc_acs_tracts))))

centroids <- centroids %>%
  mutate(GEOID = dc_acs_tracts$GEOID)

dc_acs_tracts <- left_join(x = dc_acs_tracts, y = centroids, by = "GEOID")

travel_time_sf <- left_join(x = travel_times_census_join, y = dc_acs_tracts, by = "GEOID") %>%
	st_as_sf() %>%
	st_transform(crs = 102285)
```

@@

travel_time_sf <- travel_time_sf %>%
  mutate(distance = st_distance(centroids, mnm_sf$geometry, by_element = TRUE)) %>%
  mutate(march_inaug = 0)

travel_time_sf[11122:11676, "march_inaug"] = 1
#entries 11122 to 11676
```
